Scalable Graph-Based Neural \\ Reconstruction for Connectomics

### 2018-03-13 papers/eccv2018/2_method.tex
papers: updated figures and generated results

A typical approach for generating edges produces one between all adjacent segments. Two segments $l_1$ and $l_2$ are considered adjacent if there is a pair of adjacent voxels with one labeled $l_1$ and the other labeled $l_2$.
For example, pixel-based agglomeration methods such as mean agglomeration \TODO{CITE} or waterz \TODO{CITE} consider all pairs of adjacent segments for merging.
However, this method produces too many edges in the graph for graph-based optimization approaches. 
We identify a smaller number of pairs of segments to consider as graph edges using the following approach.

>>>>

A typical approach for generating edges produces one between all adjacent segments. Two segments $l_1$ and $l_2$ are considered adjacent if there is a pair of adjacent voxels with one labeled $l_1$ and the other labeled $l_2$.
For example, pixel-based agglomeration methods such as mean agglomeration~\cite{lee2017superhuman} or waterz~\cite{funke2017deep} consider all pairs of adjacent segments for merging.
However, this method produces too many edges in the graph for graph-based optimization approaches. 
We identify a smaller number of pairs of segments to consider as graph edges using the following approach.

### 2018-03-13 papers/eccv2018/3_evaluation.tex
papers: updated figures and generated results

We use half of the Kasthuri and FlyEM datasets\footnote{Since the FlyEM datasets have significantly fewer examples, we initialize the network with the weights from the Kasthuri training and have an initial learning rate of $10^{-4}$.} for training and validation. 
We train on 80\% of the potential merge candidates for this volume.
We validate the CNN classifier on the remaining 20\% of candidates.

We consider networks with varying input sizes, optimizers, loss functions, filter sizes, learning rates, and activation functions. 
The supplemental material includes information on the experiments that determined these final parameters. 
We provide all parameters of the final network in the supplemental material. 
There are \TODO{X,XXX,XXX} learnable parameters in our final architecture. 
All the parameters are randomly initialized following the Xavier uniform distribution~\cite{glorot2010understanding}. 
Training concluded after \TODO{XXX} epochs.

@@

Since our input is an existing segmentation of the EM images, there are very few training examples compared to per-pixel classifiers that can train on a unique window for each voxel. 
The Kasthuri dataset represents a region of brain over $\SI[product-units=single]{800}{\micro\meter}^3$ in volume and only yields \TODO{700} positive merge examples and \TODO{7000} negative ones.
To avoid overfitting our deep networks, we apply the following augmentations on the training examples.
During a single batch, we randomly select ten positive and negative examples. 
With probability 0.5, the example is reflected across the $xy$-plane. 
We then rotate the example by a random angle between $0$ and $360$ degrees using nearest neighbor interpolation. 
The supplemental material contains experiments demonstrating the benefits of this augmentation strategy.
We have 20,000 such examples per epoch.

>>>>

We use half of the Kasthuri and FlyEM datasets\footnote{Since the FlyEM datasets have significantly fewer examples, we initialize the network with the weights from the Kasthuri training and have an initial learning rate of $10^{-4}$.} for training and validation. 
We train on 80\% of the potential merge candidates for this volume.
We validate the CNN classifier on the remaining 20\% of the candidates.

We consider networks with varying input sizes, optimizers, loss functions, filter sizes, learning rates, and activation functions. 
The supplemental material includes information on the experiments that determined these final parameters. 
We provide all parameters of the final network in the supplemental material. 
There are 2,313,969 learnable parameters in our final architecture. 
All the parameters are randomly initialized following the Xavier uniform distribution~\cite{glorot2010understanding}. 
Training concluded after 1000 epochs.

@@

Since our input is an existing segmentation of the EM images, there are very few training examples compared to per-pixel classifiers that can train on a unique window for each voxel. 
The Kasthuri dataset represents a region of brain over $\SI[product-units=single]{800}{\micro\meter}^3$ in volume and only yields 640 positive merge examples and 4821 negative ones.
To avoid overfitting our deep networks, we apply the following augmentations on the training examples.
During a single batch, we randomly select ten positive and negative examples. 
With probability 0.5, the example is reflected across the $xy$-plane. 
We then rotate the example by a random angle between $0$ and $360$ degrees using nearest neighbor interpolation. 
The supplemental material contains experiments demonstrating the benefits of this augmentation strategy.
We have 20,000 such examples per epoch.

### 2018-03-13 papers/eccv2018/4_results.tex
papers: updated figures and generated results

\begin{table}
	\centering
	\small
	\begin{tabular}{c c c c} \hline
		\textbf{Dataset} & \textbf{Segment Adjacency} & \textbf{Skeleton Pruning} & \textbf{Missed Split Errors} \\ \hline
		Kasthuri Training & 763 / 21,242 & 753 / 3,459 & \\
		Kasthuri Vol. 2 & 1,010 / 26,073 & 904 / 4,327 & \\
		FlyEM Vol. 1 & 269 / 14,875 & 262 / 946 & \\
		FlyEM Vol. 2 & 270 / 16,808 & 285 / 768 & \\ \hline
		%		Kasthuri Vol. 1 & 763 / 21242 (3.47\%) & 753 / 3459 (17.88\%) \\
		%		Kasthuri Vol. 2 & 1010 / 26073 (3.73\%) & 904 / 4327 (17.28\%) \\
		%		FlyEM Vol. 1 & 269 / 14875 (1.78\%) & 262 / 946 (21.69\%) \\
		%		FlyEM Vol. 2 & 270 / 16808 (1.58\%) & 285 / 768 (27.07\%)\\ \hline
	\end{tabular}
	\caption{The results of our graph pruning approach compared to the baseline graph with all adjacent regions. We show the number of true merge locations (e.g., 763) compared to total number of edges in the graph (e.g., 21,242) for each case. The number of missed splits corresponds to the number of split errors that our method misses compared to an adjacency matrix.}
	\label{table:skeletonization}
\end{table}

@@

\begin{figure}[t!]
	\centering
	\includegraphics[width=0.45\linewidth]{./figures/merge_candidate1.png}		\includegraphics[width=0.45\linewidth]{./figures/merge_candidate2.png}
	\caption{Two false negative example of our method due to graph pruning. The distance between the endpoints (circled) of the two segments is too far to be flagged as a merge candidate.}
	\label{fig:skeleton-results}
\end{figure}

@@

Data augmentation at test time can improve accuracy results~\cite{zeng2017deepem3d,lee2017superhuman}.
When computing the probability to merge two segments, we input the initial segment into our CNN as well as \TODO{XX} randomly rotated and flipped examples (in the same manner as training augmentation).
This produces some additional increase in overall accuracy (Figure ~\ref{fig:receiver-operating-characteristic}).
The supplemental material contains experiments showing the trade-offs between increased accuracy and runtime when using these augmentation strategies.

@@

\begin{table}[h]
	\centering
	\small
	\begin{tabular}{c c c c | c c c} \hline
		& \multicolumn{3}{c}{\textbf{Multicut}} & \multicolumn{3}{c}{\textbf{Lifted Multicut}} \\ \hline
		\textbf{Dataset} & $\Delta$ \textbf{Precision} & $\Delta$ \textbf{Recall} & $\Delta$ \textbf{Accuracy} & $\Delta$ \textbf{Precision} & $\Delta$ \textbf{Recall} & $\Delta$ \textbf{Accuracy} \\ \hline
		Kasthuri Training & +3.61\% & -0.53\% & +0.60\% & +3.61\% & -0.53\% & +0.60\% \\
		Kasthuri Vol. 2 & +7.59\% & -1.77\% & +1.38\%  & +7.59\% & -1.77\% & +1.38\% \\
		FlyEM Vol. 1 & +2.68\% & +0.76\% & +0.66\% & +2.68\% & +0.76\% & +0.66\% \\
		FlyEM Vol. 2 & +2.22\% & -1.05\% & +0.29\% & +2.22\% & -1.05\% & +0.29\% \\ \hline
	\end{tabular}
	\caption{Precision, recall, and accuracy changes between CNN only and CNN paired with graph-optimized reconstructions for the training and three test datasets. The combined method results in better precision and accuracy.}
	\label{table:multicut}
\end{table}

>>>>

\begin{table}
	\centering
	\small
	\setlength{\tabcolsep}{0.75em}
	\begin{tabular}{c c c c} \hline
		\textbf{Dataset} & \textbf{Segment Adjacency} & \textbf{Skeleton Pruning} & \textbf{Missed Split Errors} \\ \hline
		Kasthuri &  & & \\
		FlyEM &  &  & \\
		FIB-25 &  & & \\ \hline
	\end{tabular}
	\caption{The results of our graph pruning approach compared to the baseline graph with all adjacent regions. We show the number of true merge locations (e.g., \TODO{XXX}) compared to total number of edges in the graph (e.g., \TODO{XXXXX}) for each case. The number of missed splits corresponds to the number of split errors that our method misses compared to an adjacency matrix.}
	\label{table:skeletonization}
\end{table}

@@

\begin{figure}[t!]
	\centering
	\includegraphics[width=0.45\linewidth]{./figures/merge_candidate1.png}		\includegraphics[width=0.45\linewidth]{./figures/merge_candidate2.png}
	\caption{Two example segment pairs that we incorrectly prune from our graph. The distances between the circled endpoints are greater than our thresholds.}
	\label{fig:skeleton-results}
\end{figure}

@@

Data augmentation at test time can improve accuracy results~\cite{zeng2017deepem3d,lee2017superhuman}.
When computing the probability to merge two segments, we input the initial segment into our CNN as well as 3 randomly rotated and flipped examples (in the same manner as training augmentation).
This produces some additional increase in overall accuracy (Figure ~\ref{fig:receiver-operating-characteristic}).
The supplemental material contains experiments showing the trade-offs between increased accuracy and runtime when using these augmentation strategies.

@@

\begin{table}[h]
	\centering
	\small
	\setlength{\tabcolsep}{0.3em}
	\begin{tabular}{c c c c | c c c} \hline
		& \multicolumn{3}{c}{\textbf{Multicut}} & \multicolumn{3}{c}{\textbf{Lifted Multicut}} \\ \hline
		\textbf{Dataset} & $\Delta$ \textbf{Precision} & $\Delta$ \textbf{Recall} & $\Delta$ \textbf{Accuracy} & $\Delta$ \textbf{Precision} & $\Delta$ \textbf{Recall} & $\Delta$ \textbf{Accuracy} \\ \hline
		Kasthuri Training & +3.61\% & -0.53\% & +0.60\% & +3.61\% & -0.53\% & +0.60\% \\
		Kasthuri Vol. 2 & +7.59\% & -1.77\% & +1.38\%  & +7.59\% & -1.77\% & +1.38\% \\
		FlyEM Vol. 1 & +2.68\% & +0.76\% & +0.66\% & +2.68\% & +0.76\% & +0.66\% \\
		FlyEM Vol. 2 & +2.22\% & -1.05\% & +0.29\% & +2.22\% & -1.05\% & +0.29\% \\ \hline
	\end{tabular}
	\caption{Precision, recall, and accuracy changes between CNN only and CNN paired with graph-optimized reconstructions for the training and three test datasets. The combined method results in better precision and accuracy.}
	\label{table:multicut}
\end{table}
